Sequential algorithms to split and merge ultra-high resolution 3D images

### 2017-07-29 paper.tex
Moved simulation section

@@

@@

\subsubsection{Simulations}
After running a few simulations, we saw that the comparison between
Cluster reads and Multiple reads essentially depends on the three
Cluster reads configurations.  When Cluster reads merge incomplete
block rows (case 1), they are always outperformed by Multiple reads.
When Cluster reads merge complete block rows (case 2), the comparison
between Cluster reads and Multiple reads depends on the values of $D$
and $n$. Figure~\ref{fig:model-comparison} shows two situations where
Cluster reads and Multiple reads are alternatively better than each
other. When Cluster reads merge complete block slices (case 3),
Cluster reads and Multiple reads are equivalent.

\subsubsection{Experiments}

>>>>

\begin{itemize}
  \item In MR, no seeking withing the splits.
\end{itemize}

@@

\section{Simulations}

\todo{Make more simulations to support that claim.}
After running a few simulations, we saw that the comparison between
Cluster reads and Multiple reads essentially depends on the three
Cluster reads configurations.  When Cluster reads merge incomplete
block rows (case 1), they are always outperformed by Multiple reads.
When Cluster reads merge complete block rows (case 2), the comparison
between Cluster reads and Multiple reads depends on the values of $D$
and $n$. Figure~\ref{fig:model-comparison} shows two situations where
Cluster reads and Multiple reads are alternatively better than each
other. When Cluster reads merge complete block slices (case 3),
Cluster reads and Multiple reads are equivalent.

@@
